Let's talk about Thurstone \& Co.: An information-theoretical model for comparative judgments, and its statistical translation

### 2024-12-07 _tex/index.tex
Built site for gh-pages

\caption{\label{tbl-thurstone_cases}Thurstones cases and asumptions}

@@

\caption{\label{fig-dispersion}Discrepancies in the stimuli dispersions
and tehir effect on the distribution of the discriminal difference}

>>>>

\caption{\label{tbl-thurstone_cases}Thurstones cases and their
asumptions}

@@

\caption{\label{fig-dispersion}The Discrepancy in the dispersions of
stimuli and their effect on the distribution of the discriminal
difference}
